---
title: "Fruit Model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Running The Model

To run the model, run the file 'Fruit_model_run_with_my_data' in folder 'Run'. The parameters can be adjusted in the file 'Parameters' in folder 'Run'. The other scripts and functions involved are found in 'Analysis/Functions', 'Data/Data_Functions', 'Data/Data_Producer' and 'Model/Fruit_model'.

## Initialise

'Data_Functions.R' contains functions 'labeller', 'Data_in_final_form'.

'params.R'..

'Functions.R' contains functions 'image_tester', 'preds', 'multipreds', 'image_predictor'.

'Data_Producer.R' slow to run.

'Fruit_model.R' needs parameters, contains function 'create_fruit_model'.

```{r results='hide'}
source('~/GitHub/NIAB_Rotation/Fruit_model/Data/Data_Functions.R')
source('~/GitHub/NIAB_Rotation/Fruit_model/Run/params.R')
source('~/GitHub/NIAB_Rotation/Fruit_model/Analysis/Functions.R') 
source('~/GitHub/NIAB_Rotation/Fruit_model/Model/Fruit_model.R')  
source('~/GitHub/NIAB_Rotation/Fruit_model/Data/Data_Producer.R')
```

Data_Functions will use:

```{r eval=FALSE}
library(abind)
library(OpenImageR)
library(dplyr)
```

params will use:

```{r eval=FALSE}
library(dplyr)
```

Fruit_model will use:

``` {r eval=FALSE}
library(keras)
library(dplyr)
library(ggplot2)
library(purrr)
```

Data_Producer will use:

```{r eval=FALSE}
library(reticulate)
```

And Fruit_model_run_with_my_data will use

```{r eval=FALSE}
library(keras)
library(dplyr)
library(ggplot2)
library(tidyr)
```

## Model G

### Fit Model R

Our data comes in from script 'Data_Producer'. Now we fit the model.

```{r}
model_name <- "fruit_model_new.h5" # "fruit_model.h5"
model_my_own <-create_fruit_model(Train_data_reshaped[,,,config$channel_no,drop = F],Train_labels,Test_data_reshaped[,,,config$channel_no,drop = F],Test_labels,config$channels) # drop = F stops R collapsing array to 3 dimensions not 4
model_my_own %>% summary()
model_my_own %>% save_model_hdf5(model_name)
```

### Load Saved Model

We load saved models by using the code below.

```{r}
new_model <- load_model_hdf5(model_name)
new_model %>% summary()
```

### Test Model R

```{r}
results <- model_my_own %>% evaluate(Test_data_reshaped[,,,config$channel_no,drop=F], Test_labels)
```

### Obtain Predictions R

```{r}
data <- image_tester(internet_path,"Walnut")
```

```{r}
res2 <- model_my_own %>% predict(data)
preds(res2)
mpreds1<-multipreds(res2,number_probs)
```

## Model G

### Fit Model G
config$channel = 2
```{r results='hide', echo=FALSE}
model_name <- "fruit_model_new.h5" # "fruit_model.h5"
model_my_own <-create_fruit_model(Train_data_reshaped[,,,config$channel_no,drop = F],Train_labels,Test_data_reshaped[,,,config$channel_no,drop = F],Test_labels,config$channels) # drop = F stops R collapsing array to 3 dimensions not 4
model_my_own %>% summary()
model_my_own %>% save_model_hdf5(model_name)
```

### Test Model G

```{r results='hide', echo=FALSE}
results2 <- model_my_own %>% evaluate(Test_data_reshaped[,,,config$channel_no,drop=F], Test_labels)
```

### Obtain Predictions G

```{r results='hide', echo=FALSE}
res2 <- model_my_own %>% predict(data)
preds(res2)
mpreds2<-multipreds(res2,number_probs)
```

## Model B

### Fit Model B
config$channel = 3
```{r results='hide', echo=FALSE}
model_name <- "fruit_model_new.h5" # "fruit_model.h5"
model_my_own <-create_fruit_model(Train_data_reshaped[,,,config$channel_no,drop = F],Train_labels,Test_data_reshaped[,,,config$channel_no,drop = F],Test_labels,config$channels) # drop = F stops R collapsing array to 3 dimensions not 4
model_my_own %>% summary()
model_my_own %>% save_model_hdf5(model_name)
```

### Test Model B

```{r results='hide', echo=FALSE}
results3 <- model_my_own %>% evaluate(Test_data_reshaped[,,,config$channel_no,drop=F], Test_labels)
```

### Obtain Predictions B

```{r results='hide', echo=FALSE}
res2 <- model_my_own %>% predict(data)
preds(res2)
mpreds3<-multipreds(res2,number_probs)
```

### Fit Model RGB
config$channels = 3
config$channel  = 1:3
```{r results='hide', echo=FALSE}
model_name <- "fruit_model_new.h5" # "fruit_model.h5"
model_my_own <-create_fruit_model(Train_data_reshaped[,,,config$channel_no,drop = F],Train_labels,Test_data_reshaped[,,,config$channel_no,drop = F],Test_labels,config$channels) # drop = F stops R collapsing array to 3 dimensions not 4
model_my_own %>% summary()
model_my_own %>% save_model_hdf5(model_name)
```

### Test Model RGB

```{r results='hide', echo=FALSE}
results2 <- model_my_own %>% evaluate(Test_data_reshaped[,,,config$channel_no,drop=F], Test_labels)
```

### Obtain Predictions RGB

```{r results='hide', echo=FALSE}
res2 <- model_my_own %>% predict(data)
preds(res2)
mpreds2<-multipreds(res2,number_probs)
```

## Summary

```{r echo=FALSE}
frame<-as.data.frame(results)
frame<-rbind(frame,as.data.frame(results2),as.data.frame(results3))
colnames(frame)<-c("Loss","Accuracy")
frame$Model<-c("R only","G only","B only")
frame<-frame[c("Model","Loss","Accuracy")]
```

```{r echo=FALSE}
knitr::kable(frame, caption = "Summary")
```

```{r echo=FALSE}
knitr::kable(mpreds1, caption = "Table Of Predictions")
```
```{r echo=FALSE}
knitr::kable(mpreds2, caption = "Table Of Predictions")
```
```{r echo=FALSE}
knitr::kable(mpreds3, caption = "Table Of Predictions")
```
