---
title: "Fruit Model"
output: 
  html_document:
    toc: true
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Here we introduce the fruit classification model. The model could theoretically be adapted to for any training images containing single objects to be classified. We will first explain the purpose of each of the scripts we will be using in Section 'Initialising', before explaining how to run the model in Section 'How To Run The Model', and then exploring some of the functionality of it and what choice of colour channels and image size works best in the remainder of this file.

## Initialising

'params.R' contains the parameters we will need. These are then put into a list and called using params$parameter_name. These are broken down by file/path parameters, fruit label numbers we want to test, and model parameters. The file/path parameters will specify which folders we want to extract the images from. The label numbers will specify which fruits we are intend to include in the model. The model parameters will prescribe things like image size, number of training epochs, and which colour channels we want to use in model training.

'Data_Functions.R' contains functions 'labeller', 'Data_in_final_form'. These are used to import the images we use to train or test our model. They produce an array with slices corresponding to the intensities of the R, G and B channels for each particular image. We also obtain a list of labels corresponding to these images.

'Cluster_data_functions.R' is an updated version of 'Data_Functions.R' that is designed to run in parallel. On this laptop, using 7 cores, we obtain a run time that is nearly 7 times faster than the original script was. We can check this using the command 'system.time()'.

'Functions.R' contains functions 'image_tester', 'preds', 'multipreds', 'image_predictor'. These functions allow us to feed in an image and obtain probabilities assigned by the model that the image belongs to a particular category. Function 'multipreds', for example, will give up to n predictions of which category the image belongs to, in descending order of likelihood, where n is specified by 'params$number_probs'.

'Data_Producer.R' is slow to run. Currently set up to run in parallel which is faster than the commented out older version which used 'Data_Functions.R' which was not parallelized. It uses functions from 'Cluster_data_functions.R' to produce and save the test and training data we will need for the model.

'Fruit_model.R' contains function 'create_fruit_model'. This gives the full description of the model.

Another file that is in the `Fruit_model' folder is 'Bigger_model/Master_model'. This is an initial mock up of how we might fit a multinomial logistic regression once we have obtained our image recognition predictions. This contains some made-up data that might be representative of data that would be the input of our eventual model. However this will likely be replaced with something more sophisticated like an SVM?

```{r results='hide'}
source('~/GitHub/NIAB_Rotation/Fruit_model/Run/params.R')
source('~/GitHub/NIAB_Rotation/Fruit_model/Data/Data_Functions.R')
source('~/GitHub/NIAB_Rotation/Fruit_model/Data/Cluster_data_Functions.R')
source('~/GitHub/NIAB_Rotation/Fruit_model/Analysis/Functions.R') 
source('~/GitHub/NIAB_Rotation/Fruit_model/Model/Fruit_model.R')
```

```{r, echo=FALSE}
evaluate_scripts <- TRUE
evaluate_scripts2<- TRUE
```

```{r, eval=evaluate_scripts}
source('~/GitHub/NIAB_Rotation/Fruit_model/Data/Data_Producer.R')
```

Data_Functions will use:

```{r eval=FALSE}
library(abind)
library(OpenImageR)
library(dplyr)
```

params will use:

```{r eval=FALSE}
library(dplyr)
```

Fruit_model will use:

``` {r eval=FALSE}
library(keras)
library(dplyr)
library(ggplot2)
library(purrr)
```

Data_Producer will use:

```{r eval=FALSE}
library(reticulate)
```

And Fruit_model_run_with_my_data will use

```{r eval=FALSE}
library(keras)
library(dplyr)
library(ggplot2)
library(tidyr)
```

We can load the data files previously saved by script 'Data_producer'.

```{r}
Train_data_saved   <- readRDS("fruit_train_data.Rda")
Train_labels_saved <- readRDS("fruit_train_labels.Rda")
Test_data_saved    <- readRDS("fruit_test_data.Rda")
Test_labels_saved  <- readRDS("fruit_test_labels.Rda")
```


The model is set up to identify single fruits - it has not been trained on images with multiple fruits and the probabilities it gives sum to 1 for prediciting individual fruits.

## How To Run The Model

If we simply run the file 'Fruit_model_run_with_my_data.R', with whatever parameters we want to specify in the 'params.R' file, then we will fit a model that can distinguish between the fruit types specified by 'labels_to_be_tested'. This data and the model will be saved, which can be loaded at a later date provided we save it with a unique file name that doesn't get overwritten. We can also test our model against any .jpeg image obtained online or otherwise and saved within a folder that we can access via changing 'internet_path' and 'internet_file_type' and specifying the folder name.

```{r eval=FALSE}
data <- image_tester(params$internet_path,"Braeburn")
res2 <- model_my_own %>% predict(data)
preds(res2)
multipreds(res2,params$number_probs)
```






## Analysis

## Comparison Between Colour Choices

### Model, Channel R

#### Fit Model, Channel R

Our data comes in from script 'Data_Producer'. Now we fit the model.

```{r}
params$channel_no = 1
```

```{r, eval=evaluate_scripts}
model_my_own <-create_fruit_model(Train_data_saved[,,,params$channel_no,drop = F],Train_labels_saved,Test_data_saved[,,,params$channel_no,drop = F],Test_labels_saved)
model_my_own %>% summary()
model_my_own %>% save_model_hdf5("fruit_model_r.h5")
```

#### Load Saved Model

We load saved models by using the code below.

```{r}
model_r <- load_model_hdf5("fruit_model_r.h5")
model_r %>% summary()
```

#### Test Model, Channel R

```{r}
results_r <- model_r %>% evaluate(Test_data_saved[,,,params$channel_no,drop=F], Test_labels_saved)
```

#### Obtain Predictions For Model, Channel R

```{r}
data <- image_tester(internet_path,"Banana")
```

```{r}
res_r <- model_r %>% predict(data)
preds(res_r)
mpreds_r<-multipreds(res_r,number_probs)
```
```{r echo=FALSE}
knitr::kable(mpreds_r, caption = "Table Of Predictions R")
```



### Model, Channel G

#### Fit Model, Channel G

```{r}
params$channel_no = 2
```

```{r results='hide', echo=FALSE, eval=evaluate_scripts}
model_g <-create_fruit_model(Train_data_saved[,,,params$channel_no,drop = F],Train_labels_saved,Test_data_saved[,,,params$channel_no,drop = F],Test_labels_saved)
model_g %>% summary()
model_g %>% save_model_hdf5("fruit_model_g.h5")
```

```{r}
model_g <- load_model_hdf5("fruit_model_g.h5")
model_g %>% summary()
```


<!-- #### Test Model, Channel G -->

```{r results='hide', echo=FALSE}
results_g <- model_g %>% evaluate(Test_data_saved[,,,params$channel_no,drop=F], Test_labels_saved)
```

<!-- #### Obtain Predictions For Model, Channel G -->

```{r results='hide', echo=FALSE}
res_g <- model_g %>% predict(data)
preds(res_g)
mpreds_g<-multipreds(res_g,number_probs)
```

```{r echo=FALSE}
knitr::kable(mpreds_g, caption = "Table Of Predictions G")
```



### Model, Channel B

#### Fit Model, Channel B

```{r}
params$channel = 3
```

```{r results='hide', echo=FALSE, eval=evaluate_scripts}
model_b <-create_fruit_model(Train_data_saved[,,,params$channel_no,drop = F],Train_labels_saved,Test_data_saved[,,,params$channel_no,drop = F],Test_labels_saved)
model_b %>% summary()
model_b %>% save_model_hdf5("fruit_model_b.h5")
```

```{r}
model_b <- load_model_hdf5("fruit_model_b.h5")
model_b %>% summary()
```


<!-- #### Test Model, Channel B -->

```{r results='hide', echo=FALSE}
results_b <- model_b %>% evaluate(Test_data_saved[,,,params$channel_no,drop=F], Test_labels_saved)
```

<!-- #### Obtain Predictions For Model, Channel B -->

```{r results='hide', echo=FALSE}
res_b <- model_b %>% predict(data)
preds(res_b)
mpreds_b<-multipreds(res_b,number_probs)
```

```{r echo=FALSE}
knitr::kable(mpreds_b, caption = "Table Of Predictions B")
```


### Model, Channels RG

```{r}
params$channel_no  = 1:2
```

#### Fit Model, Channels RG

```{r results='hide', echo=FALSE, eval=evaluate_scripts}
model_rg <-create_fruit_model(Train_data_saved[,,,params$channel_no,drop = F],Train_labels_saved,Test_data_saved[,,,params$channel_no,drop = F],Test_labels_saved)
model_rg %>% summary()
model_rg %>% save_model_hdf5("fruit_model_rg.h5")
```

```{r}
model_rg <- load_model_hdf5("fruit_model_rg.h5")
model_rg %>% summary()
```

<!-- #### Test Model, Channels RG -->

```{r results='hide', echo=FALSE}
results_rg <- model_rg %>% evaluate(Test_data_saved[,,,params$channel_no,drop=F], Test_labels_saved)
```

<!-- #### Obtain Predictions For Model, Channels RG -->

```{r results='hide', echo=FALSE}
data <- image_tester(internet_path,"Banana")
```

```{r results='hide', echo=FALSE}
res_rg <- model_rg %>% predict(data)
preds(res_rg)
mpreds_rg<-multipreds(res_rg,number_probs)
```

```{r echo=FALSE}
knitr::kable(mpreds_rg, caption = "Table Of Predictions RG")
```


### Model, Channels RGB

```{r}
params$channel_no  = 1:3
```

#### Fit Model, Channels RGB


```{r results='hide', echo=FALSE, eval=evaluate_scripts}
model_rgb <-create_fruit_model(Train_data_saved[,,,params$channel_no,drop = F],Train_labels_saved,Test_data_saved[,,,params$channel_no,drop = F],Test_labels_saved)
model_rgb %>% summary()
model_rgb %>% save_model_hdf5("fruit_model_rgb.h5")
```

```{r}
model_rgb <- load_model_hdf5("fruit_model_rgb.h5")
model_rgb %>% summary()
```

<!-- #### Test Model, Channels RGB -->

```{r results='hide', echo=FALSE}
results_rgb <- model_rgb %>% evaluate(Test_data_saved[,,,params$channel_no,drop=F], Test_labels_saved)
```

<!-- #### Obtain Predictions For Model, Channels RGB -->

```{r results='hide', echo=FALSE}
data <- image_tester(internet_path,"Banana")
```

```{r results='hide', echo=FALSE}
res_rgb <- model_rgb %>% predict(data)
preds(res_rgb)
mpreds_rgb<-multipreds(res_rgb,number_probs)
```

```{r echo=FALSE}
knitr::kable(mpreds_rgb, caption = "Table Of Predictions RGB")
```


### Summary Of Colour Channel Choices

```{r echo=FALSE}
frame<-as.data.frame(results_r)
frame<-rbind(frame,as.data.frame(results_g),as.data.frame(results_b),as.data.frame(results_rg),as.data.frame(results_rgb))
colnames(frame)<-c("Loss","Accuracy")
frame$Model<-c("R only","G only","B only","RG","RGB")
frame<-frame[c("Model","Loss","Accuracy")]
```

```{r echo=FALSE}
knitr::kable(frame, caption = "Summary")
```



## Comparison of Image Sizes

### 100 x 100

```{r results='hide', eval=evaluate_scripts2}
params$xshape <- 100
params$yshape <- 100
params$train_data_name  <- "fruit_train_data100.Rda"
params$train_label_name <- "fruit_train_labels100.Rda"
params$test_data_name   <- "fruit_test_data100.Rda"
params$test_label_name  <- "fruit_test_labels100.Rda"


###

Train_data_and_labels <- Data_in_final_form(params$pathname,params$training_folder,params$labels_to_be_tested,params$filetype)

Train_data <-Train_data_and_labels$Image_array
Train_data <- aperm(Train_data,c(3,1,2)) # reorders elements
Train_labels <- Train_data_and_labels$label_vector[,1]
Train_total  <- length(Train_labels)
####

Test_data_and_labels <- Data_in_final_form(params$pathname,params$test_folder,params$labels_to_be_tested,params$filetype)

Test_data <-Test_data_and_labels$Image_array
Test_data <- aperm(Test_data,c(3,1,2)) # reorders elements
Test_labels <- Test_data_and_labels$label_vector[,1]
Test_total  <- length(Test_labels)

############################################

Train_data_reshaped <- array_reshape(Train_data,c(Train_total,params$xshape,params$yshape,3),order=c("F"))
Test_data_reshaped  <- array_reshape(Test_data,c(Test_total,params$xshape,params$yshape,3),order=c("F"))

saveRDS(Train_data_reshaped,file=params$train_data_name)
saveRDS(Train_labels,file=params$train_label_name)
saveRDS(Test_data_reshaped,file=params$test_data_name)
saveRDS(Test_labels,file=params$test_label_name)
```

```{r}
Train_data_saved <- readRDS("fruit_train_data100.Rda")
Train_labels_saved <- readRDS("fruit_train_labels100.Rda")
Test_data_saved <- readRDS("fruit_test_data100.Rda")
Test_labels_saved <- readRDS("fruit_test_labels100.Rda")
```

```{r results='hide', echo=FALSE, eval=evaluate_scripts2}
model_rgb100 <-create_fruit_model(Train_data_saved[,,,params$channel_no,drop = F],Train_labels_saved,Test_data_saved[,,,params$channel_no,drop = F],Test_labels_saved) # drop = F stops R collapsing array to 3 dimensions not 4
model_rgb100 %>% summary()
model_rgb100 %>% save_model_hdf5("fruit_model_rgb100.h5")
```


```{r}
model_rgb100 <- load_model_hdf5("fruit_model_rgb100.h5")
model_rgb100 %>% summary()
```


```{r results='hide'}
results_rgb100 <- model_rgb100 %>% evaluate(Test_data_saved[,,,params$channel_no,drop=F], Test_labels_saved)
```

### 50 x 50

```{r echo=FALSE, results='hide', eval=evaluate_scripts2}
params$xshape <- 50
params$yshape <- 50
params$train_data_name  <- "fruit_train_data50.Rda"
params$train_label_name <- "fruit_train_labels50.Rda"
params$test_data_name   <- "fruit_test_data50.Rda"
params$test_label_name  <- "fruit_test_labels50.Rda"


###

Train_data_and_labels <- Data_in_final_form(params$pathname,params$training_folder,params$labels_to_be_tested,params$filetype)

Train_data <-Train_data_and_labels$Image_array
Train_data <- aperm(Train_data,c(3,1,2)) # reorders elements
Train_labels <- Train_data_and_labels$label_vector[,1]
Train_total  <- length(Train_labels)
####

Test_data_and_labels <- Data_in_final_form(params$pathname,params$test_folder,params$labels_to_be_tested,params$filetype)

Test_data <-Test_data_and_labels$Image_array
Test_data <- aperm(Test_data,c(3,1,2)) # reorders elements
Test_labels <- Test_data_and_labels$label_vector[,1]
Test_total  <- length(Test_labels)

############################################

Train_data_reshaped <- array_reshape(Train_data,c(Train_total,params$xshape,params$yshape,3),order=c("F"))
Test_data_reshaped  <- array_reshape(Test_data,c(Test_total,params$xshape,params$yshape,3),order=c("F"))

saveRDS(Train_data_reshaped,file=params$train_data_name)
saveRDS(Train_labels,file=params$train_label_name)
saveRDS(Test_data_reshaped,file=params$test_data_name)
saveRDS(Test_labels,file=params$test_label_name)
```

```{r, echo=FALSE}
Train_data_saved   <- readRDS("fruit_train_data50.Rda")
Train_labels_saved <- readRDS("fruit_train_labels50.Rda")
Test_data_saved    <- readRDS("fruit_test_data50.Rda")
Test_labels_saved  <- readRDS("fruit_test_labels50.Rda")
```

```{r results='hide', echo=FALSE, eval=evaluate_scripts2}
model_rgb50 <-create_fruit_model(Train_data_saved[,,,params$channel_no,drop = F],Train_labels_saved,Test_data_saved[,,,params$channel_no,drop = F],Test_labels_saved) # drop = F stops R collapsing array to 3 dimensions not 4
model_rgb50 %>% summary()
model_rgb50 %>% save_model_hdf5("fruit_model_rgb50.h5")
```

```{r}
model_rgb50 <- load_model_hdf5("fruit_model_rgb50.h5")
model_rgb50 %>% summary()
```


```{r results='hide', echo=FALSE}
results_rgb50 <- model_rgb50 %>% evaluate(Test_data_saved[,,,params$channel_no,drop=F], Test_labels_saved)
```

### 28 x 28

```{r echo=FALSE, results='hide', eval=evaluate_scripts2}
params$xshape <- 28
params$yshape <- 28
params$train_data_name  <- "fruit_train_data28.Rda"
params$train_label_name <- "fruit_train_labels28.Rda"
params$test_data_name   <- "fruit_test_data28.Rda"
params$test_label_name  <- "fruit_test_labels28.Rda"


###

Train_data_and_labels <- Data_in_final_form(params$pathname,params$training_folder,params$labels_to_be_tested,params$filetype)

Train_data <-Train_data_and_labels$Image_array
Train_data <- aperm(Train_data,c(3,1,2)) # reorders elements
Train_labels <- Train_data_and_labels$label_vector[,1]
Train_total  <- length(Train_labels)
####

Test_data_and_labels <- Data_in_final_form(params$pathname,params$test_folder,params$labels_to_be_tested,params$filetype)

Test_data <-Test_data_and_labels$Image_array
Test_data <- aperm(Test_data,c(3,1,2)) # reorders elements
Test_labels <- Test_data_and_labels$label_vector[,1]
Test_total  <- length(Test_labels)

############################################

Train_data_reshaped <- array_reshape(Train_data,c(Train_total,params$xshape,params$yshape,3),order=c("F"))
Test_data_reshaped  <- array_reshape(Test_data,c(Test_total,params$xshape,params$yshape,3),order=c("F"))

saveRDS(Train_data_reshaped,file=params$train_data_name)
saveRDS(Train_labels,file=params$train_label_name)
saveRDS(Test_data_reshaped,file=params$test_data_name)
saveRDS(Test_labels,file=params$test_label_name)
```

```{r, echo=FALSE}
Train_data_saved   <- readRDS("fruit_train_data28.Rda")
Train_labels_saved <- readRDS("fruit_train_labels28.Rda")
Test_data_saved    <- readRDS("fruit_test_data28.Rda")
Test_labels_saved  <- readRDS("fruit_test_labels28.Rda")
```

```{r results='hide', echo=FALSE, eval=evaluate_scripts2}
model_rgb28 <-create_fruit_model(Train_data_saved[,,,params$channel_no,drop = F],Train_labels_saved,Test_data_saved[,,,params$channel_no,drop = F],Test_labels_saved) # drop = F stops R collapsing array to 3 dimensions not 4
model_rgb28 %>% summary()
model_rgb28 %>% save_model_hdf5("fruit_model_rgb28.h5")
```


```{r}
model_rgb28 <- load_model_hdf5("fruit_model_rgb28.h5")
model_rgb28 %>% summary()
```


```{r results='hide', echo=FALSE}
results_rgb28 <- model_rgb28 %>% evaluate(Test_data_saved[,,,params$channel_no,drop=F], Test_labels_saved)
```

### 12 x 12

```{r echo=FALSE, results='hide', eval=evaluate_scripts2}
params$xshape <- 12
params$yshape <- 12
params$train_data_name  <- "fruit_train_data12.Rda"
params$train_label_name <- "fruit_train_labels12.Rda"
params$test_data_name   <- "fruit_test_data12.Rda"
params$test_label_name  <- "fruit_test_labels12.Rda"


###

Train_data_and_labels <- Data_in_final_form(params$pathname,params$training_folder,params$labels_to_be_tested,params$filetype)

Train_data <-Train_data_and_labels$Image_array
Train_data <- aperm(Train_data,c(3,1,2)) # reorders elements
Train_labels <- Train_data_and_labels$label_vector[,1]
Train_total  <- length(Train_labels)
####

Test_data_and_labels <- Data_in_final_form(params$pathname,params$test_folder,params$labels_to_be_tested,params$filetype)

Test_data <-Test_data_and_labels$Image_array
Test_data <- aperm(Test_data,c(3,1,2)) # reorders elements
Test_labels <- Test_data_and_labels$label_vector[,1]
Test_total  <- length(Test_labels)

############################################

Train_data_reshaped <- array_reshape(Train_data,c(Train_total,params$xshape,params$yshape,3),order=c("F"))
Test_data_reshaped  <- array_reshape(Test_data,c(Test_total,params$xshape,params$yshape,3),order=c("F"))

saveRDS(Train_data_reshaped,file=params$train_data_name)
saveRDS(Train_labels,file=params$train_label_name)
saveRDS(Test_data_reshaped,file=params$test_data_name)
saveRDS(Test_labels,file=params$test_label_name)
```

```{r, echo=FALSE}
Train_data_saved   <- readRDS("fruit_train_data12.Rda")
Train_labels_saved <- readRDS("fruit_train_labels12.Rda")
Test_data_saved    <- readRDS("fruit_test_data12.Rda")
Test_labels_saved  <- readRDS("fruit_test_labels12.Rda")
```

```{r results='hide', echo=FALSE, eval=evaluate_scripts2}
model_rgb12 <-create_fruit_model(Train_data_saved[,,,params$channel_no,drop = F],Train_labels_saved,Test_data_saved[,,,params$channel_no,drop = F],Test_labels_saved) # drop = F stops R collapsing array to 3 dimensions not 4
model_rgb12 %>% summary()
model_rgb12 %>% save_model_hdf5("fruit_model_rgb12.h5")
```


```{r}
model_rgb12 <- load_model_hdf5("fruit_model_rgb12.h5")
model_rgb12 %>% summary()
```


```{r results='hide', echo=FALSE}
results_rgb12 <- model_rgb12 %>% evaluate(Test_data_saved[,,,params$channel_no,drop=F], Test_labels_saved)
```

### Summary Of Image Size Choice

```{r echo=FALSE}
frame<-as.data.frame(results_rgb100)
frame<-rbind(frame,as.data.frame(results_rgb50),as.data.frame(results_rgb28),as.data.frame(results_rgb12))
colnames(frame)<-c("Loss","Accuracy")
frame$Image_Size<-c("100","50","28","12")
frame<-frame[c("Image_Size","Loss","Accuracy")]
colnames(frame)<-c("Image_Size" ,"Loss","Accuracy")
```

```{r echo=FALSE}
knitr::kable(frame, caption = "RGB model, different image sizes")
```